---
title: "Multiple Regression and Backward Selection"
output: html_notebook
---



```{r}
library(readr)
Data= read_csv("50_Startups.csv")
View(Data)
```

```{r}
Data
```

```{r}
# Encoding categorical data
# factor function converts categorical to numerical but sees the values as factors

Data$State=factor(Data$State,
                  levels=c("New York","California","Florida"),
                  labels = c(1,2,3))
```


```{r}
# split the data
library(caTools)
```


```{r}
set.seed(123) # random state
split = sample.split(Data$Profit, SplitRatio = 0.8)
#specifing the trainig set. True is for the trainig set
training_set = subset(Data,split==TRUE)
test_set = subset(Data,split==FALSE)
```


```{r}
#Fit the Multiple Linear Regressor
regressor = lm( formula = Profit ~ . , data=training_set)

```


```{r}
summary(regressor)
```

```{r}
# Predict the test results
y_pred = predict(regressor, newdata = test_set)
y_pred
```

# Backward Elimination, Step by Step
Drop independent variable that have a pvalue greater than 0.05%

STEPS
1.Select a significance level to stay in the model (S.L = 0.05)
2.Fit the full model with all possible predictors
3.Consider the predictor with the highest p-values ie above 0.05
4.Remove the predictor
5.Fit the model without the prdictor

Iterate steps 3 ,4 and 5 until non of the predictor p_values is greater than 0.05.
```{r}
# We can see from the result above only the R and D spend as a significant impact on the profit oof each startup.
# Buil the optimal model using backward elimination step by step
regressor1 = lm( formula = Profit ~ `R&D Spend` + Administration + `Marketing Spend` + State , data=Data)

summary(regressor1)
```


```{r}
# The highest p_value from the result above is in the state- Califonia, so we would take out the state since Florida is also not significant.
regressor2 = lm( formula = Profit ~ `R&D Spend` + Administration + `Marketing Spend`, data=Data)

summary(regressor2)

```


```{r}
# The next predictor to remove is Administration
regressor3 = lm( formula = Profit ~ `R&D Spend` + `Marketing Spend` , data=Data)

summary(regressor3)
```


```{r}
# The last one is the Marketing Spend, even though the p-value is small and almost at 0.05 we would remove it because it doesnt meet the mark
regressor3 = lm( formula = Profit ~ `R&D Spend`, data=Data)

summary(regressor3)
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

